Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives

### 2016-07-13 summary.tex
last modified

\subsubsection{Intersects on face edges}
When intersection line segment lies on an edge (Fig. \ref{fig:twin}). we call it as \emph{edge intersections}. When there are edge intersections, the intersection line segment will be inserted several times, requiring extra effort to eliminate repetitions. Also, as edge intersections lies on the edge, their intersection contexts are edges, not faces. Finally, in some configurations, edge intersections will cause non-manifold surface as isolated intersection point does, which have to be detected and carefully handled.

There are generally two kinds of edge intersections. If $\gamma(f_1)$ lies on the edge of $f_1$ or $f_2$, but on the inside the face of the other one, then we called it as edge-face intersections (Fig. \ref{fig:twin}(a), (b), (c)). If $l$ lies on the edges of both $f_1$ and $f_2$, we call it as edge-edge intersections (Fig. \ref{fig:twin}(e), (f), (g)). To eliminate repetitive intersection records, when there is edge-face intersection, we treat it as the intersection of three faces $f_1$, $f_2$ and $f_1^\star$ (or $f_2^\star$). When there is edge-edge intersection, we treat it as the intersection of four faces $f_1$, $f_2$, $f_1^\star$ and $f_2^\star$. The $f_1^\star$ (or $f_2^\star$), known as \emph{companion face},  is the neighboring face which shares the intersection edge with $f_1$ (or $f_2$).

@@

Both edge-face and edge-edge intersection can be further classified into three subclasses by the location of companion faces---cross condition, coplanar condition and invalid condition. We first consider edge-face intersection. Without generality, assume $f_1$ and $f_2$ intersect on the edge of $f_1$ and there is a companion face $f_1^\star$. If $f_1$ and $f_1^\star$ are on the same side of $f_2$, it is cross condition. If they are on the same side, it is invalid condition. If $f_1^\star$ is coplanar with $f_2$, it is coplanar condition. Consider the cross and coplanar condition. For $f_2$, the IR is the same as the common situation, except that the intersection context is an edge. For $f_1$ and $f_1^\star$, they have to share the intersection line segment, while the intersection context is $f_2$.  However, when there is invalid condition, we should not record the intersection for the similar reasons of isolated point intersection (section \ref{sec:ipoint}).

>>>>

\subsubsection{Intersects on face edges}
When intersection line segment lies on an edge (Fig. \ref{fig:twin}). we call it as \emph{edge intersections}. There are generally two kinds of edge intersections. If $\gamma$ lies on the edge of $f_1$ or $f_2$, but inside of the face of the other one, then we called it as edge-face intersections. If $\gamma$ lies on the edges of both $f_1$ and $f_2$, we call it as edge-edge intersections. When there is edge-face intersection, we treat it as the intersection of three faces $f_1$, $f_2$ and $f_1^\star$ (or $f_2^\star$). When there is edge-edge intersection, we treat it as the intersection of four faces $f_1$, $f_2$, $f_1^\star$ and $f_2^\star$. The $f_1^\star$ (or $f_2^\star$), known as \emph{companion face},  is the neighboring face which shares the intersection edge with $f_1$ (or $f_2$). In this way, we avoid repetitive insertion of the same edge intersections, since the companion faces share the same intersection with its neighborhood $f_1$ or $f_2$.

@@

Both edge-face and edge-edge intersection can be further classified into three subclasses by the location of companion faces---cross condition, coplanar condition and invalid condition. We first consider edge-face intersection. If $f_1$ and $f_1^\star$ are on the same side of $f_2$, it is cross condition. If they are on the same side, it is invalid condition. If $f_1^\star$ is coplanar with $f_2$, it is coplanar condition. Consider the cross and coplanar condition. For $f_2$, the IR is the same as the common situation, except that the intersection context is an edge. For $f_1$ and $f_1^\star$, they have to share the intersection line segment, while the intersection context is $f_2$.  However, when there is invalid condition, we should not record the intersection for the similar reasons of isolated point intersection (section \ref{sec:ipoint}).
